GEE models

### 2017-09-29 doc/manuscript.Rmd
Remove total label from facet_grid (gee)

```{r figure2_gee_unadj, fig.cap=fig_gee_unadj}
gee_results %>% 
    dplyr::filter(model == "Unadjusted") %>% 
    plot_gee_main()
```

```{r figure3_gee_adj, fig.cap=fig_gee_adj}
gee_results %>% 
    dplyr::filter(model == "Adjusted") %>% 
    plot_gee_main()
```

>>>>

```{r figure2_gee_unadj, fig.cap=fig_gee_unadj}
gee_results %>% 
    dplyr::filter(model == "Unadjusted") %>% 
    dplyr::mutate(unit = ifelse(unit == "Total", " ", unit)) %>% 
    plot_gee_main()
```

```{r figure3_gee_adj, fig.cap=fig_gee_adj}
gee_results %>% 
    dplyr::filter(model == "Adjusted") %>% 
    dplyr::mutate(unit = ifelse(unit == "Total", " ", unit)) %>% 
    plot_gee_main()
```
